Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-05-18 Paper/Paper.tex
fixed my name!

% Three addresses
% --------------
\threeauthors
  {Thierry Bertin-Mahieux} {Columbia University\\ {\tt tb2332@columbia.edu}}
  {Ron Weiss} {New York University \\ {\tt ronw@nyu.edu}}
  {Dan Ellis} {Columbia University \\ {\tt dpwe@ee.columbia.edu}}
% what order do we use? Thierry, Ron, Dan?  Dan, Thierry, Ron?

>>>>

% Three addresses
% --------------
\threeauthors
  {Thierry Bertin-Mahieux} {Columbia University\\ {\tt tb2332@columbia.edu}}
  {Ron J. Weiss} {New York University \\ {\tt ronw@nyu.edu}}
  {Dan Ellis} {Columbia University \\ {\tt dpwe@ee.columbia.edu}}
% what order do we use? Thierry, Ron, Dan?  Dan, Thierry, Ron?
